Symmetric Circuits for Rank Gates

### 2018-02-28 sections/translating-formulas-to-cicuits.tex
Updates to the entire paper 28th Feb 2018

\documentclass[../paper.tex]{subfiles}
\begin{document}
In this section we first introduce a number of useful polynomial-time computable
functions which define transformations on circuits. In the second subsection we
use these functions to define a transformation that takes $\FPR$-formulas to
equivalent families of transparent symmetric rank-circuits.

\subsection{Algorithms for Circuits}
In order to simplify the presentation of the translation between $P$-uniform
families of circuits and formulas of $\FPR$, as well as the proofs of other
results (see Lemma~\ref{lem:transparent-unique}), we define a number of
often-used polynomial-time computable circuit transformations.

We first define the function $\op{merge}$, which maps a circuit and a set of
syntactically-equivalent gates to a circuit formed by combining those gates into
a single gate.

\begin{definition}
  Let $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ be a circuit and $H
  := \{h_1, \ldots, h_p\}$ be a set of syntactically equivalent gates. We let
  $\op{merge}(C, H) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
  \rangle$, where
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $G' = G \setminus \{h_2, \ldots, h_p\}$,
  \item $\Omega' = \Omega$,
  \item $\Sigma' = \restr{\Sigma}{G'}$,
  \item $\Lambda' = \Lambda$, and
  \item For all $g \in G'$ and $x \in Ind(g)$ if $L(g) (x) \in H$ then $L'(g)(x)
    = h_1$ and if $L(g)(x) \notin H$ then $L'(g)(x) = L(g)(x)$.
  \end{itemize}
\end{definition}

It can be shown that $\op{merge}$ can be computed in time polynomial in the size
of the input circuit. We note that the input and output circuits compute the
same function. Moreover, if the input circuit is symmetric (resp. has unique
labels, is transparent) then the output circuit will also be symmetric (resp.
have unique labels, transparent).

We now define the function $\op{merge-all}$ which maps a circuit and a set of
gates to a new circuit formed by applying $\op{merge}$ to the
syntactic-equivalence classes of the set of gates.

\begin{definition}
  \label{def:merge-all}
  The function $\op{merge-all}$ maps a circuit $C$ and a set of gates $H$ to a
  circuit $\op{merge-all}(C, H) := C'$, where $C'$ is defined as follows. Let
  $H_1, \ldots, H_p$ be the syntactic equivalence classes of $H$, and let $C'$
  be defined from $C$ by successively applying $\op{merge}$ to each of these
  equivalence classes.
\end{definition}

We can compute $\op{merge-all}$ using the following algorithm. Let $(C, H)$ be a
tuple in the domain of $\op{merge-all}$. We assume a reasonable encoding of the
circuit, and note that any such encoding induces a linear order on the
structure. Let $H_1, \ldots, H_p$ be the syntactic-equivalence classes of $H$
linearly ordered such that for all $i, j \in [p]$ if $i \leq j$ the height of
the gates in $H_i$ is less than or equal to the height of the gates in $H_j$.
Let $C'$ be the result of successively executing the algorithm for $\op{merge}$
on each such equivalence class in order.

It is worth noting that for an input tuple $(C, H)$, if follows from
Lemma~\cite{lem:unique-labels-syntactic-equiv} that if $H$ has unique labels
then the syntactic-equivalence relation on $H$ can be computed in time
polynomial in the size of $C$. Thus, if each gate in $H$ has unique labels, it
can be shown that $\op{merge-all}$ can be computed in time polynomial in the
size of the input circuit.

As in the case of $\op{merge}$, the function $\op{merge-all}$ preserves
symmetry, unique labels and the ensures that the input and output circuits
compute the same function. Let be a circuit $C$ a circuit and $H$ a set of gates
in $C$ with unique labels. Then if $g$ is a gate in both $C$ and $C' :=
\op{merge-all}(C, H)$, and all of the children of $g$ in $C$ are in $H$, then no
two distinct children of $g$ in $C'$ are syntactically-equivalent. However, we
have no guarantee that $g$ will have unique labels in $C'$ as we have no
guarantee that $L'(g)$ is injective.

The now define the function $\op{make-injective}$ that maps a circuit and a
symmetric gate to an equivalent circuit containing all the same gates as the
input circuit but such that the specified gate now has injective labels.

\begin{definition}
  \label{def:make-injective}
  The function $\op{make-injective}$ maps a circuit $C := \langle G, \Omega,
  \Sigma , \Lambda, L \rangle$ and a gate $h \in G$ to the circuit
  $\op{make-injective}(C, h) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
  \rangle$, defined as follows. Let $c = \max \{\vert L(g)^{-1}(h)\vert : g \in
  W(h, \cdot)\}$. If $c = 1$ then $C' := C$. If $c > 1$ then $C'$ is defined
  such that
  \begin{itemizens}
  \item $G' = G \uplus \{h_2, \ldots, h_{c-1}\}$,
  \item $\Omega' = \Omega$,
  \item For each $g \in G$ let $\Sigma' (g) = \Sigma(g)$, otherwise let
    $\Sigma'(g)$ be a single-input $\AND$-gate.
  \item $\Lambda'= \Lambda$
  \item For each $g \in G'$ if $g \in G \setminus W(h, \cdot)$ then $L'(g) =
    L(g)$. If $g \in W(h, \cdot)$ let $\{x_1, \ldots, x_k\} := L(g)^{-1}(h)$ and
    for each $x \in \ind(g)$ if $L(g)(x) \neq h$ then $L'(g)(x) = L(g)(x)$ else
    if $x = x_i \in L(g)^{-1}(h)$ then let $L'(g)(x) = h_i$.
  \end{itemizens}
\end{definition}

It can be shown that $\op{make-injective}$ can be computed by an algorithm
running in time polynomial in the size of the input circuit. Moreover, the input
and output circuits of this operation compute the same function.

We now define the function $\op{make-injective-all}$ that maps a circuit to an
equivalent circuit such that every symmetric gate now has injective labels.

\begin{definition}
  The function $\op{make-injective-all}$ maps a circuit $C := \langle G, \Omega,
  \Sigma , \Lambda, L \rangle$ to a circuit $\op{make-injective}(C) := C' :=
  \langle G', \Omega', \Sigma', \Lambda', L' \rangle$ defined as follows.

  Let $F$ be a function that maps an ordered circuit $C*$ to the circuit
  $\op{make-injective}(C*, h)$, where $h$ is the topologically first gate such
  that there exists a gate $g$ in $C*$ where $h$ is a child of $g$ and $\vert
  L*(g)^{-1}(h) \vert > 1$. Let $(C^0, C^1, \ldots)$ be a sequence of circuits
  where $C^0 := C$ and for $i > 1$, $C^i := F(C^{i-1})$. It can be shown that
  this sequence converges after at most $\vert C \vert$ many steps. Let $C'$ be
  the limit of this sequence.
\end{definition}

Since $\op{make-injective}$ can be computed in polynomial time, and the number
of iterations required to converge to the limit in the above definition is
bounded by the size of the circuit, it can be shown that
$\op{make-injective-all}$ can be computed in time polynomial in the size of the
input circuit. Furthermore, we note that $\op{make-injective-all}$ preserves
symmetry, rigidity and unique labels. Moreover, the input and output circuits
compute the same function.

We now define the function $\op{insert}$ that maps two circuits to a circuit
formed by inserting the gates of the first circuit into the second circuit.

\begin{definition}
  The function $\op{insert}$ maps a $(\mathbb{B}_1, \tau_1)$-circuit $C^1 :=
  \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1 \rangle$ and a
  $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2, \Sigma_2 ,
  \Lambda_2, L_2 \rangle$ to a $(\mathbb{B}_1 \cup \mathbb{B}_2, \tau_1 \uplus
  \tau_2)$-circuit $\op{insert}(C^1, C^2) := C := \langle G, \Omega, \Sigma ,
  \Lambda, L \rangle$, where
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $G = G_1 \uplus G_2$,
  \item $\Omega = \Omega_2$,
  \item $\Sigma = \Sigma_1 \uplus \Sigma_2$,
  \item $\Lambda = \Lambda_1 \uplus \Lambda_2$, and
  \item $L = L_1 \uplus L_2$.
  \end{itemize}
\end{definition}

It can be shown that $\op{insert}$ can be be computed in time polynomial in the
size of the input circuits. Moreover, if the input circuits are symmetric then
the output circuit is symmetric.

We now define the function $\op{replace}$ that maps a circuit $C$ and a pair of
gates $(g_1, g_2)$ in $C$ to a circuit $C'$ formed by replacing $g_1$ with $g_2$
in $C$.

\begin{definition}
  The function $\op{replace}$ maps a circuit $C = \langle G, \Omega, \Sigma,
  \Lambda, L\rangle$ and a pair of gates $(g_1, g_2)$ in $C$ to a circuit
  $\op{replace}(C, g_1, g_2) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
  \rangle$, where
  \begin{itemize}
    \setlength\itemsep{0mm}
  \item $G' = G \setminus \{g_1\}$,
  \item $\Omega'$ is an function from the domain of $\Omega$ to $G'$ such that
    for each $\vec{a} \in \dom(\Omega)$ if $\Omega(\vec{a}) = g_1$ then
    $\Omega'(\vec{a}) = g_2$ and otherwise $\Omega'(\vec{a}) = \Omega(\vec{a})$.
  \item $\Sigma' = \restr{\Sigma}{G'}$
  \item $\Lambda' = \restr{\Lambda}{G'}$
  \item For each $g \in G'$ and each $x \in \ind(g)$ if $L(g)(x) = g_1$ then
    $L'(g)(x) = g_2$ and if not then $L'(g)(x) = L(g)(x)$.
  \end{itemize}
\end{definition}

It can be shown that the function $\op{replace}$ can be computed in time
polynomial in the size of the input circuit.

We now define the function $\op{tag}$ that maps a circuit, a relation symbol, a
gate in that circuit, and a tuple to a circuit computing the same function as
the input circuit but with an additional gadget, constructed using the gates
labelled by the given relation symbol and tuple, marking the designated gate.
The intuition is that this marking helps to distinguish a gate, and is used as a
step to ensure that a circuit has unique labels.

\begin{definition}
  The function $\op{tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle G,
  \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation symbol $R \in
  \tau$, a gate $g \in G$, and a tuple $\vec{a} \in [n]^k$ for some $k$ to a
  circuit $\op{tag}(C, R, g, \vec{a}) := C' := \langle G', \Omega', \Sigma',
  \Lambda', L'\rangle$ of order $n$, such that $G' = G \uplus \{\land_g,
  \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda' =
  \Lambda$. For each $g \in G$ $\Sigma'(g) = \Sigma(g)$. For each $g \in
  \{\land_0, \land_1, \ldots , \land_k \}$, $\Sigma(g)$ is an $\AND$-gate that
  takes in two inputs. $\Sigma(\land_g)$ is an $\AND$-gate that takes in a
  single input, $g$ is the lone input to $\land_g$, and $\land_0$ has as input
  $\land_g$ and $\land_1$. For each $i \in [k-1]$ the inputs of $\land_i$ are
  $\land_{i+1}$ and the gate $g_i \in G'$ such that $\Sigma(g_i) = R$ and
  $\Lambda^{-1}(g_i) = \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple
  $(\vec{a}(i), \ldots, \vec{a}(i))$. The inputs of $\land_k$ are the constant
  gate $1$ and the gate $g_k$ such that $\Sigma(g) = R$ and $\Lambda^{-1}(g_k) =
  \vec{a}_k$. For each gate $h \in G \setminus \{g\}$ and $x \in \ind(h)$, if
  $L(h)(x) = g$ then $L'(h)(x) = \land_0$, otherwise $L'(h)(x) = L(h)(x)$.
\end{definition}

It can be shown that $\op{tag}$ can be computed in time polynomial in the size
of its input. The input and output circuits compute the same function. Moreover,
if the input circuit has unique labels then the output circuit will have unique
labels. If the input relation symbol is obvious from the context we omit it when
invoking $\op{tag}$.

\begin{definition}
  The function $\op{tag-all}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle
  G, \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation symbol $R \in
  \tau$, a set of gates $H \subseteq G$, and $T := (\vec{a}_h)_{h \in H}
  \subseteq [n]^{k}$ a sequence of tuples indexed by $H$ for some fixed $k$, to
  a circuit $\op{tag-all}(C, R, H, T) := C' := \langle G', \Omega', \Sigma',
  \Lambda', L'\rangle$ of order $n$ defined as follows.

  Suppose there is a linear order on $H$, and write $H = \{h_1, \ldots, h_t\}$.
  Let $C_0 := C$ and for all $i \in [t]$ let $C_i := \op{tag}(C_{i-1}, R, h_i,
  T(h_i))$. Then $C' = C_{t}$.
\end{definition}

It is easy to see that, since $\op{tag}$ can be computed in time polynomial in
the combined size of its inputs, $\op{tag-all}$ can also be computed in time
polynomial in the combined size of its inputs.

We now define the function $\op{compose}$ that maps a circuit and a sequence of
circuits and to a circuit formed by replacing the input gates of the designated
circuit with the output gates of the circuits in the sequence.

\begin{definition}
  The function $\op{compose}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle
  G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation sybmols $\tau_R
  := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a sequence of
  circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i \in [t]$,
  $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
  $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and $C^i$
  computes a query of arity $\arty(R_i)$ to a circuit $\op{compose}(C,
  \mathcal{C}, \tau_R) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
  \rangle$. Note that all circuits take in structures of size $n$. The circuit
  $C'$ is defined as follows.

  Let ${C^0}' := \langle G_0', \Omega_0', \Sigma_0', \Lambda_0', L_0' \rangle :=
  C$, and let $i \in [t]$. Let $D^{i-1}:= \op{insert} (C^i, {C^{i-1}}')$ and
  $G^{i-1}_{R_i}$ be the set of all relational gates in $D^{i-1}$ labelled by
  the relational symbol in $R_i$. Let ${C^{i-1}}' := \langle G_i', \Omega_i',
  \Sigma_i', \Lambda_i', L_i' \rangle$ be the circuit formed from $D^{i-1}$ by
  replacing each gate in $g \in G^{i-1}_{R_i}$ with the gate
  $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ (by repeated calls to the
  $\op{replace}$ function). Let $C' = {C^{t}}'$.
\end{definition}

It can be shown that $\op{compose}$ can be computed in time polynomial in the
sum of the sizes of the input circuits. We also note that the size of $C'$ is
less than or equal to the sum of the sizes of the input circuits. Moreover, if
the input circuits are all symmetric then the output circuit will be symmetric.
Also, for an input tuple $(C, \mathcal{C}, \tau_R)$, we have that if $C$ has
symmetric gates and transparent, and all the circuits in $\mathcal{C}$ are
transparent, then $C' := \op{compose}(C, \mathcal{C}, \tau_R)$ is transparent.
If $C$ contains a non-symmetric gates then, as the output gates of the circuits
in $\mathcal{C}$ are no longer labelled as output gates in $C'$, it may be that
some of these gates are syntactically-equivalent in $C'$, resulting in $C'$ not
being transparent.

In certain contexts we are interested composing gates such that if the input
circuits are transparent (resp. have unique labels) then the output circuits
will be transparent (resp. have unique labels). In this case, while composing
the circuits we apply the $\op{tag}$ function to the output gates of the
circuits in the input sequence of circuits. We now define the function
$\op{compose-and-tag}$ that implements this operation.

\begin{definition}
  The function $\op{compose-and-tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
  \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation symbols
  $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a sequence
  of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i \in [t]$,
  $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is a
  $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and $C^i$
  computes a query of arity $\arty(R_i)$ to a circuit $\op{compose-and-tag}(C,
  \mathcal{C}, \tau_R, R) := C'$. The circuit $C'$ is defined as follows. Note
  that all circuits take in structures of size $n$.

  Let $D^0 := \op{compose}(C, \mathcal{C}, \tau_R)$. For each $i \in [t]$, let
  $D^{i} := \op{tag-all}(D^{i-1}, R, \img(\Omega^{-1}_i), \Omega^{-1}_i)$. Let
  $C' := D^t$.
\end{definition}

>>>>

\documentclass[../paper.tex]{subfiles}
\begin{document}
% In this section we first introduce a number of useful polynomial-time
% computable functions which define transformations on circuits. In the second
% subsection we use these functions to define a transformation that takes
% $\FPR$-formulas to equivalent families of transparent symmetric rank-circuits.

% \subsection{Algorithms for Circuits}
% In order to simplify the presentation of the translation between $P$-uniform
% families of circuits and formulas of $\FPR$, as well as the proofs of other
% results (see Lemma~\ref{lem:transparent-unique}), we define a number of
% often-used polynomial-time computable circuit transformations.

% We first define the function $\op{merge}$, which maps a circuit and a set of
% syntactically-equivalent gates to a circuit formed by combining those gates
% into a single gate.

% \begin{definition}
%   Let $C := \langle G, \Omega, \Sigma , \Lambda, L \rangle$ be a circuit and
%   $H := \{h_1, \ldots, h_p\}$ be a set of syntactically equivalent gates. We
%   let $\op{merge}(C, H) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
%   \rangle$, where
%   \begin{itemize}
%     \setlength\itemsep{0mm}
%   \item $G' = G \setminus \{h_2, \ldots, h_p\}$,
%   \item $\Omega' = \Omega$,
%   \item $\Sigma' = \restr{\Sigma}{G'}$,
%   \item $\Lambda' = \Lambda$, and
%   \item For all $g \in G'$ and $x \in Ind(g)$ if $L(g) (x) \in H$ then
%     $L'(g)(x) = h_1$ and if $L(g)(x) \notin H$ then $L'(g)(x) = L(g)(x)$.
%   \end{itemize}
% \end{definition}

% It can be shown that $\op{merge}$ can be computed in time polynomial in the
% size of the input circuit. We note that the input and output circuits compute
% the same function. Moreover, if the input circuit is symmetric (resp. has
% unique labels, is transparent) then the output circuit will also be symmetric
% (resp. have unique labels, transparent).

% We now define the function $\op{merge-all}$ which maps a circuit and a set of
% gates to a new circuit formed by applying $\op{merge}$ to the
% syntactic-equivalence classes of the set of gates.

% \begin{definition}
%   \label{def:merge-all}
%   The function $\op{merge-all}$ maps a circuit $C$ and a set of gates $H$ to a
%   circuit $\op{merge-all}(C, H) := C'$, where $C'$ is defined as follows. Let
%   $H_1, \ldots, H_p$ be the syntactic equivalence classes of $H$, and let $C'$
%   be defined from $C$ by successively applying $\op{merge}$ to each of these
%   equivalence classes.
% \end{definition}

% We can compute $\op{merge-all}$ using the following algorithm. Let $(C, H)$ be
% a tuple in the domain of $\op{merge-all}$. We assume a reasonable encoding of
% the circuit, and note that any such encoding induces a linear order on the
% structure. Let $H_1, \ldots, H_p$ be the syntactic-equivalence classes of $H$
% linearly ordered such that for all $i, j \in [p]$ if $i \leq j$ the height of
% the gates in $H_i$ is less than or equal to the height of the gates in $H_j$.
% Let $C'$ be the result of successively executing the algorithm for
% $\op{merge}$ on each such equivalence class in order.

% It is worth noting that for an input tuple $(C, H)$, if follows from
% Lemma~\cite{lem:unique-labels-syntactic-equiv} that if $H$ has unique labels
% then the syntactic-equivalence relation on $H$ can be computed in time
% polynomial in the size of $C$. Thus, if each gate in $H$ has unique labels, it
% can be shown that $\op{merge-all}$ can be computed in time polynomial in the
% size of the input circuit.

% As in the case of $\op{merge}$, the function $\op{merge-all}$ preserves
% symmetry, unique labels and the ensures that the input and output circuits
% compute the same function. Let be a circuit $C$ a circuit and $H$ a set of
% gates in $C$ with unique labels. Then if $g$ is a gate in both $C$ and $C' :=
% \op{merge-all}(C, H)$, and all of the children of $g$ in $C$ are in $H$, then
% no two distinct children of $g$ in $C'$ are syntactically-equivalent. However,
% we have no guarantee that $g$ will have unique labels in $C'$ as we have no
% guarantee that $L'(g)$ is injective.

% The now define the function $\op{make-injective}$ that maps a circuit and a
% symmetric gate to an equivalent circuit containing all the same gates as the
% input circuit but such that the specified gate now has injective labels.

% \begin{definition}
%   \label{def:make-injective}
%   The function $\op{make-injective}$ maps a circuit $C := \langle G, \Omega,
%   \Sigma , \Lambda, L \rangle$ and a gate $h \in G$ to the circuit
%   $\op{make-injective}(C, h) := C' := \langle G', \Omega', \Sigma', \Lambda',
%   L' \rangle$, defined as follows. Let $c = \max \{\vert L(g)^{-1}(h)\vert : g
%   \in W(h, \cdot)\}$. If $c = 1$ then $C' := C$. If $c > 1$ then $C'$ is
%   defined such that
%   \begin{itemizens}
%   \item $G' = G \uplus \{h_2, \ldots, h_{c-1}\}$,
%   \item $\Omega' = \Omega$,
%   \item For each $g \in G$ let $\Sigma' (g) = \Sigma(g)$, otherwise let
%     $\Sigma'(g)$ be a single-input $\AND$-gate.
%   \item $\Lambda'= \Lambda$
%   \item For each $g \in G'$ if $g \in G \setminus W(h, \cdot)$ then $L'(g) =
%     L(g)$. If $g \in W(h, \cdot)$ let $\{x_1, \ldots, x_k\} := L(g)^{-1}(h)$
%     and for each $x \in \ind(g)$ if $L(g)(x) \neq h$ then $L'(g)(x) = L(g)(x)$
%     else if $x = x_i \in L(g)^{-1}(h)$ then let $L'(g)(x) = h_i$.
%   \end{itemizens}
% \end{definition}

% It can be shown that $\op{make-injective}$ can be computed by an algorithm
% running in time polynomial in the size of the input circuit. Moreover, the
% input and output circuits of this operation compute the same function.

% We now define the function $\op{make-injective-all}$ that maps a circuit to an
% equivalent circuit such that every symmetric gate now has injective labels.

% \begin{definition}
%   The function $\op{make-injective-all}$ maps a circuit $C := \langle G,
%   \Omega, \Sigma , \Lambda, L \rangle$ to a circuit $\op{make-injective}(C) :=
%   C' := \langle G', \Omega', \Sigma', \Lambda', L' \rangle$ defined as
%   follows.

%   Let $F$ be a function that maps an ordered circuit $C*$ to the circuit
%   $\op{make-injective}(C*, h)$, where $h$ is the topologically first gate such
%   that there exists a gate $g$ in $C*$ where $h$ is a child of $g$ and $\vert
%   L*(g)^{-1}(h) \vert > 1$. Let $(C^0, C^1, \ldots)$ be a sequence of circuits
%   where $C^0 := C$ and for $i > 1$, $C^i := F(C^{i-1})$. It can be shown that
%   this sequence converges after at most $\vert C \vert$ many steps. Let $C'$
%   be the limit of this sequence.
% \end{definition}

% Since $\op{make-injective}$ can be computed in polynomial time, and the number
% of iterations required to converge to the limit in the above definition is
% bounded by the size of the circuit, it can be shown that
% $\op{make-injective-all}$ can be computed in time polynomial in the size of
% the input circuit. Furthermore, we note that $\op{make-injective-all}$
% preserves symmetry, rigidity and unique labels. Moreover, the input and output
% circuits compute the same function.

% We now define the function $\op{insert}$ that maps two circuits to a circuit
% formed by inserting the gates of the first circuit into the second circuit.

% \begin{definition}
%   The function $\op{insert}$ maps a $(\mathbb{B}_1, \tau_1)$-circuit $C^1 :=
%   \langle G_1, \Omega_1, \Sigma_1 , \Lambda_1, L_1 \rangle$ and a
%   $(\mathbb{B}_2, \tau_2)$-circuit $C^2 := \langle G_2, \Omega_2, \Sigma_2 ,
%   \Lambda_2, L_2 \rangle$ to a $(\mathbb{B}_1 \cup \mathbb{B}_2, \tau_1 \uplus
%   \tau_2)$-circuit $\op{insert}(C^1, C^2) := C := \langle G, \Omega, \Sigma ,
%   \Lambda, L \rangle$, where
%   \begin{itemize}
%     \setlength\itemsep{0mm}
%   \item $G = G_1 \uplus G_2$,
%   \item $\Omega = \Omega_2$,
%   \item $\Sigma = \Sigma_1 \uplus \Sigma_2$,
%   \item $\Lambda = \Lambda_1 \uplus \Lambda_2$, and
%   \item $L = L_1 \uplus L_2$.
%   \end{itemize}
% \end{definition}

% It can be shown that $\op{insert}$ can be be computed in time polynomial in
% the size of the input circuits. Moreover, if the input circuits are symmetric
% then the output circuit is symmetric.

% We now define the function $\op{replace}$ that maps a circuit $C$ and a pair
% of gates $(g_1, g_2)$ in $C$ to a circuit $C'$ formed by replacing $g_1$ with
% $g_2$ in $C$.

% \begin{definition}
%   The function $\op{replace}$ maps a circuit $C = \langle G, \Omega, \Sigma,
%   \Lambda, L\rangle$ and a pair of gates $(g_1, g_2)$ in $C$ to a circuit
%   $\op{replace}(C, g_1, g_2) := C' := \langle G', \Omega', \Sigma', \Lambda',
%   L' \rangle$, where
%   \begin{itemize}
%     \setlength\itemsep{0mm}
%   \item $G' = G \setminus \{g_1\}$,
%   \item $\Omega'$ is an function from the domain of $\Omega$ to $G'$ such that
%     for each $\vec{a} \in \dom(\Omega)$ if $\Omega(\vec{a}) = g_1$ then
%     $\Omega'(\vec{a}) = g_2$ and otherwise $\Omega'(\vec{a}) =
%     \Omega(\vec{a})$.
%   \item $\Sigma' = \restr{\Sigma}{G'}$
%   \item $\Lambda' = \restr{\Lambda}{G'}$
%   \item For each $g \in G'$ and each $x \in \ind(g)$ if $L(g)(x) = g_1$ then
%     $L'(g)(x) = g_2$ and if not then $L'(g)(x) = L(g)(x)$.
%   \end{itemize}
% \end{definition}

% It can be shown that the function $\op{replace}$ can be computed in time
% polynomial in the size of the input circuit.

% We now define the function $\op{tag}$ that maps a circuit, a relation symbol,
% a gate in that circuit, and a tuple to a circuit computing the same function
% as the input circuit but with an additional gadget, constructed using the
% gates labelled by the given relation symbol and tuple, marking the designated
% gate. The intuition is that this marking helps to distinguish a gate, and is
% used as a step to ensure that a circuit has unique labels.

% \begin{definition}
%   The function $\op{tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C := \langle G,
%   \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation symbol $R \in
%   \tau$, a gate $g \in G$, and a tuple $\vec{a} \in [n]^k$ for some $k$ to a
%   circuit $\op{tag}(C, R, g, \vec{a}) := C' := \langle G', \Omega', \Sigma',
%   \Lambda', L'\rangle$ of order $n$, such that $G' = G \uplus \{\land_g,
%   \land_{g'}, \land_1, \ldots , \land_k\}$, $\Omega' = \Omega$, and $\Lambda'
%   = \Lambda$. For each $g \in G$ $\Sigma'(g) = \Sigma(g)$. For each $g \in
%   \{\land_0, \land_1, \ldots , \land_k \}$, $\Sigma(g)$ is an $\AND$-gate that
%   takes in two inputs. $\Sigma(\land_g)$ is an $\AND$-gate that takes in a
%   single input, $g$ is the lone input to $\land_g$, and $\land_0$ has as input
%   $\land_g$ and $\land_1$. For each $i \in [k-1]$ the inputs of $\land_i$ are
%   $\land_{i+1}$ and the gate $g_i \in G'$ such that $\Sigma(g_i) = R$ and
%   $\Lambda^{-1}(g_i) = \vec{a}_i$, where $\vec{a}_i$ is the $k$-tuple
%   $(\vec{a}(i), \ldots, \vec{a}(i))$. The inputs of $\land_k$ are the constant
%   gate $1$ and the gate $g_k$ such that $\Sigma(g) = R$ and $\Lambda^{-1}(g_k)
%   = \vec{a}_k$. For each gate $h \in G \setminus \{g\}$ and $x \in \ind(h)$,
%   if $L(h)(x) = g$ then $L'(h)(x) = \land_0$, otherwise $L'(h)(x) = L(h)(x)$.
% \end{definition}

% It can be shown that $\op{tag}$ can be computed in time polynomial in the size
% of its input. The input and output circuits compute the same function.
% Moreover, if the input circuit has unique labels then the output circuit will
% have unique labels. If the input relation symbol is obvious from the context
% we omit it when invoking $\op{tag}$.

% \begin{definition}
%   The function $\op{tag-all}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
%   \langle G, \Omega, \Sigma, \Lambda, L \rangle$ of order $n$, a relation
%   symbol $R \in \tau$, a set of gates $H \subseteq G$, and $T :=
%   (\vec{a}_h)_{h \in H} \subseteq [n]^{k}$ a sequence of tuples indexed by $H$
%   for some fixed $k$, to a circuit $\op{tag-all}(C, R, H, T) := C' := \langle
%   G', \Omega', \Sigma', \Lambda', L'\rangle$ of order $n$ defined as follows.

%   Suppose there is a linear order on $H$, and write $H = \{h_1, \ldots,
%   h_t\}$. Let $C_0 := C$ and for all $i \in [t]$ let $C_i := \op{tag}(C_{i-1},
%   R, h_i, T(h_i))$. Then $C' = C_{t}$.
% \end{definition}

% It is easy to see that, since $\op{tag}$ can be computed in time polynomial in
% the combined size of its inputs, $\op{tag-all}$ can also be computed in time
% polynomial in the combined size of its inputs.

% We now define the function $\op{compose}$ that maps a circuit and a sequence
% of circuits and to a circuit formed by replacing the input gates of the
% designated circuit with the output gates of the circuits in the sequence.

% \begin{definition}
%   The function $\op{compose}$ maps a $(\mathbb{B}, \tau)$-circuit $C :=
%   \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation
%   sybmols $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a
%   sequence of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i
%   \in [t]$, $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is
%   a $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and
%   $C^i$ computes a query of arity $\arty(R_i)$ to a circuit $\op{compose}(C,
%   \mathcal{C}, \tau_R) := C' := \langle G', \Omega', \Sigma', \Lambda', L'
%   \rangle$. Note that all circuits take in structures of size $n$. The circuit
%   $C'$ is defined as follows.

%   Let ${C^0}' := \langle G_0', \Omega_0', \Sigma_0', \Lambda_0', L_0' \rangle
%   := C$, and let $i \in [t]$. Let $D^{i-1}:= \op{insert} (C^i, {C^{i-1}}')$
%   and $G^{i-1}_{R_i}$ be the set of all relational gates in $D^{i-1}$ labelled
%   by the relational symbol in $R_i$. Let ${C^{i-1}}' := \langle G_i',
%   \Omega_i', \Sigma_i', \Lambda_i', L_i' \rangle$ be the circuit formed from
%   $D^{i-1}$ by replacing each gate in $g \in G^{i-1}_{R_i}$ with the gate
%   $\Omega_{i}(\Lambda_{i-1}'(g))$ in $D^{i-1}$ (by repeated calls to the
%   $\op{replace}$ function). Let $C' = {C^{t}}'$.
% \end{definition}

% It can be shown that $\op{compose}$ can be computed in time polynomial in the
% sum of the sizes of the input circuits. We also note that the size of $C'$ is
% less than or equal to the sum of the sizes of the input circuits. Moreover, if
% the input circuits are all symmetric then the output circuit will be
% symmetric. Also, for an input tuple $(C, \mathcal{C}, \tau_R)$, we have that
% if $C$ has symmetric gates and transparent, and all the circuits in
% $\mathcal{C}$ are transparent, then $C' := \op{compose}(C, \mathcal{C},
% \tau_R)$ is transparent. If $C$ contains a non-symmetric gates then, as the
% output gates of the circuits in $\mathcal{C}$ are no longer labelled as output
% gates in $C'$, it may be that some of these gates are syntactically-equivalent
% in $C'$, resulting in $C'$ not being transparent.

% In certain contexts we are interested composing gates such that if the input
% circuits are transparent (resp. have unique labels) then the output circuits
% will be transparent (resp. have unique labels). In this case, while composing
% the circuits we apply the $\op{tag}$ function to the output gates of the
% circuits in the input sequence of circuits. We now define the function
% $\op{compose-and-tag}$ that implements this operation.

% \begin{definition}
%   The function $\op{compose-and-tag}$ maps a $(\mathbb{B}, \tau)$-circuit $C
%   := \langle G, \Omega, \Sigma, \Lambda, L \rangle$, a sequence of relation
%   symbols $\tau_R := (R_1, \ldots, R_t)$ such that $\tau_R \subseteq \tau$, a
%   sequence of circuits $\mathcal{C} := ( C^1, \ldots, C^t)$, where for each $i
%   \in [t]$, $C^i = \langle G_i, \Omega_i, \Sigma_i, \Lambda_i, L_i \rangle$ is
%   a $(\mathbb{B}_i, \tau_i)$-circuit, and $\tau_i \not\subset \tau_R$ and
%   $C^i$ computes a query of arity $\arty(R_i)$ to a circuit
%   $\op{compose-and-tag}(C, \mathcal{C}, \tau_R, R) := C'$. The circuit $C'$ is
%   defined as follows. Note that all circuits take in structures of size $n$.
